mir\_eval

### 2014-05-01 paper/paper.tex
Adding results table with garbage values

\documentclass{article}
\usepackage{ismir2014,amsmath,cite}
\usepackage{graphicx}
\usepackage{dsfont}
\usepackage{stmaryrd}
\usepackage{braket}
%\usepackage{authblk}

@@

>>>>

\documentclass{article}
\usepackage{ismir2014,amsmath,cite}
\usepackage{graphicx}
\usepackage{dsfont}
\usepackage{stmaryrd}
\usepackage{braket}
%\usepackage{authblk}
\usepackage{booktabs}

@@

% Compared each mir_eval task to an existing implementation
% Parameterized the same wherever possible

% Beat: Compared against MIREX 2013
% Chord: Compared against ??
% Segmentation: Compared against ??
% Melody: Compared against MIREX 2011, SG2 only
% Pattern: Compared against development set, MATLAB code
% Source Separation: Compared against SiSEC dev sets
% Onset: Compared against MIREX 2013

\begin{table*}[t]
  \centering
\begin{tabular}{c c c c c c c c c}
\toprule
 \multicolumn{9}{ c }{Beat Tracking} \\
  \cmidrule(lr){1-9}
 F-Measure  &  Cemgil   &   Goto    &    P-score & CMLc     &     CMLt       &   AMLc     &     AMLt    &      D (bits)\\
 0.00659 & 0.00035 & 0.00060  & 0.00877 & 0.00157 & 0.00135 & 0.00137&  0.00135 & 0.10566\\
  \midrule
 \multicolumn{5}{ c }{Chord Recognition} & \multicolumn{4}{ c }{Something else}  \\
  \cmidrule(lr){1-5}
  \cmidrule(lr){6-9}
 Root  &  Maj/Min   &   Maj/Min + Inv    &     Sevenths     &     Sevenths + Inv & CMLt      &   AMLc     &     AMLt    &      D (bits)\\
 ??? & ??? & ???  & ??? & ??? & 0.00135 & 0.00137&  0.00135 & 0.10566\\
  \midrule
 \multicolumn{3}{ c }{Onset Detection} & \multicolumn{6}{ c }{Blah}  \\
  \cmidrule(lr){1-3}
  \cmidrule(lr){4-9}
 F-Measure  &  Precision   &  Recall    &     McKinney P-s & CMLc     &     CMLt       &   AMLc     &     AMLt    &      D (bits)\\
 0.00203 & 0.00202 & 0.00203  & 0.00877 & 0.00157 & 0.00135 & 0.00137&  0.00135 & 0.10566\\
  \bottomrule

\end{tabular}
\end{table*}
